DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-02 paper/evaluation.tex
..

Figure~\ref{fig:} shows the normalized execution time and L2 miss-rate
of the DNN model running on the Core 0 as a function of the number of
co-scheduled memory intensive synthetic benchmarks. First, as we
increase the number of co-runners, the DNN model's execution times are
increased---by up to 11.6X---even though the DNN model is running on a
dedicated core (Core 0). On the other hand, the DNN model's L2
cache-miss rates do not increase as much.
In other words, the DNN model's execution increase is not fully
explained by increased contention in the L2 cache space.
Instead, the high memory bandwidth pressure from the co-scheduled
memory intensive benchmarks is likely the primary cause.

>>>>

Figure~\ref{fig:} shows the normalized execution time (first group) and
L2 miss-rate (last group)
of the DNN model running on the Core 0 as a function of the number of
co-scheduled memory intensive synthetic benchmarks. We also shows the
normalized total system bus access count (middle group), which is
representative of memory bandwidth usage of all the cores.
First, as we
increase the number of co-runners, the DNN model's execution times are
increased exponentially---by up to 11.6X---even though the DNN model
is running on a dedicated core (Core 0). On the other hand, the DNN
model's L2 cache-miss rates do not increase as much.
In other words, the DNN model's execution increase is not fully
explained by increased contention in the L2 cache space.
Instead, the exponential increase in the total number of bus accesses,
due to the memory-hog co-runners, appears to be more closely
correlated with the DNN model's execution time increase. This is
the high memory bandwidth pressure from the co-scheduled
memory intensive benchmarks would have increased the DNN model's
memory access latency.
